A Dependently Typed Multi-Stage Calculus\thanks{Supported by organization x.}

### 2019-05-26 main.tex
Wrote until preservation.

\begin{theorem}[Preservation for term on $\beta$ reduction]
	If $\G\V M:\tau @A$ and $M \longrightarrow_{\beta} M'$, then $\G\V M':\tau @A$\\
\end{theorem}

\begin{theorem}[Preservation for term on $\TBL\TB$ reduction]
	If $\G\V M:\tau @A$ and $M\longrightarrow_\blacklozenge N$, then $\G\V N:\tau @A$\\
\end{theorem}

\begin{theorem}[Preservation for term on $\Lambda$ reduction]
	If $\G\V M:\tau @A$ and $M \longrightarrow_{\Lambda} N$, then $\G\V N:\tau @A$.
\end{theorem}

\begin{theorem}[Strong Normalization]
	If $\G\V^A t:T$ then there is no infinite sequence of terms $(t_i)_{i\ge1}$ and $t_i \longrightarrow_{\beta, \TBL \TB,\Lambda} t_{i+1}$ for $i\ge 1$
\end{theorem}

>>>>

\begin{theorem}[Preservation]
	If $\G\V M:\tau @A$ and $M \longrightarrow M'$, then $\G\V M':\tau @A$\\
\end{theorem}

\begin{theorem}[Strong Normalization]
	If $\G\V^A M:\tau$ then there is no infinite sequence of terms $(M_i)_{i\ge1}$ and 
	$M_i \longrightarrow M_{i+1}$ for $i\ge 1$
\end{theorem}
